17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-23 rules/rules22.tex
read over the proof section again

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script,
\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
a single argument and run the solver on the benchmark.
%
As described in Section~\ref{sec:logistics}, the benchmark
will contains the commands \akey{(check-sat)} and \akey{(get-proof)}.
%
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

@@

\header{Input/Output Checker.}
The second script, \texttt{starexec\_checker\_default}, takes as input
the benchmark file name as first argument and the stdout output of the
solver script as second argument.  Note that this output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

The checker should check the proof within the output and provide the result to
stdout.
%
A result printed to stderr is ignored.
%
The first line of the proof checker result should be either \texttt{valid},
\texttt{invalid}, \texttt{holey}, \texttt{sat}, or \texttt{unknown}.
%
The answer \texttt{valid} must only be given when the checker certifies the
given proof justifies the unsatisfiability of the given benchmark.
%
A checker that returns \texttt{valid} to a satisfiable benchmark is deemed to be
unsound.
%
The answer \texttt{invalid} should be returned if the proof is errorneous or
otherwise malformed.
%
If the proof checker determines that the proof is valid but it contains holes,
i.e., steps that are not checked for correctness, the answer should be
\texttt{holey}.
%
The answer \texttt{sat} should be given if the solver claimed that the benchmark
is satisfiable, and \texttt{unknown} should be given if the solver answered
\texttt{unknown}, if it answered \texttt{unsat} but did not give a proof, or if
the solver gave an error result.

@@

\header{Result.}
%
The result of a solver is considered \emph{erroneous} if (i) the
response to the \akey{check-sat} command is \texttt{sat} (as the
benchmark is necessarily unsatisfiable), or
%
(ii) the proof checker returns \texttt{invalid} to
the given proof.
%
Since the \prooftrack is non-competitive and we are not fixing a definition of a
valid proof, there will be no score computed for this track.

>>>>

\header{Input/Output Solver.}
For the \prooftrack, solver authors should provide two scripts
with their solver.  The first script,
\texttt{starexec\_solver\_default}, should take the name of the benchmark file as
a single argument and run the solver on the benchmark.
%
As described in Section~\ref{sec:logistics}, the benchmark
will contain the commands \akey{(check-sat)} and \akey{(get-proof)}.
%
The solver must output the answers to both of these commands to stdout.
Output to stderr is ignored by the toolchain.

@@

\header{Input/Output Checker.}
The second script, \texttt{starexec\_checker\_default}, should take
the benchmark file name as first argument and the stdout output of the
solver script as second argument.  Note that this output will
usually start with the \texttt{unsat} result of the \akey{(check-sat)}
command, which the checker must either parse or skip.

The checker should check the proof within the output and provide the result to
stdout.
%
Output printed to stderr is ignored.
%
The first line of the proof checker result should be either \texttt{valid},
\texttt{invalid}, \texttt{holey}, \texttt{sat}, or \texttt{unknown}.
%
The answer \texttt{valid} must only be given when the checker certifies that the
given proof justifies the unsatisfiability of the given benchmark.
%
A checker that returns \texttt{valid} to a satisfiable benchmark is deemed to be
unsound.
%
The answer \texttt{invalid} should be returned if the proof is errorneous or
otherwise malformed.
%
If the proof checker determines that the proof is valid but it contains holes,
i.e., steps that are not checked for correctness, the answer should be
\texttt{holey}.
%
The answer \texttt{sat} should be given if the solver claimed that the benchmark
is satisfiable, and \texttt{unknown} should be given if (1) the solver answered
\texttt{unknown}, (2) it answered \texttt{unsat} but did not give a proof, or 
(3) if the solver gave an error result.

@@

\header{Result.}
%
The result of a solver is considered \emph{erroneous} if (i) the
proof checker returns \texttt{sat} (as the
benchmark is necessarily unsatisfiable), or
%
(ii) the proof checker returns \texttt{invalid} to
the given proof.
%
Since the \prooftrack is non-competitive and we are not fixing a definition of a
valid proof, there will be no score computed for this track.
